Central Limit Theorems for Super Ornstein-Uhlenbeck Processes with stable Branching

### 2019-01-31 supCLT.tex
supCLT.tex: version 3

% supCLT1.tex 2018/6/24 by Zhenyao

@@

@@

\email{???@pku.edu.cn}

@@

%We first fix our notation, for a vector $x\in \mathbb{R}^d$, we denote by $|x|$  its Euclidean norm. Let $\xi=\{\xi_t : t\geq 0\}$ be an Ornstein-Uhlenbeck prcess, short for OU process, on $\mathbb{R}^d$, with infinitesimal generator $L$. For any $f \in C^2(\mathbb{R}^d)$,
%\begin{equation}\label{generatior}
%Lf(x)= \frac{1}{2}\sigma^2\Delta f(x)-b (x \cdot \nabla f(x))   
%where $\sigma>0$ is the diffusion parameter, $b>0$ is the drift parameters. What's more, we respectively use $\Delta$ and $\nabla$ to express the Laplace operator and gradient operator as usual.

@@

\begin{equation}\label{generatior}

@@

    %= \frac{1}{2}\sigma^2\Delta f(x)-b (x \cdot \nabla f(x)), 

@@

%For any $x\in \mathbb{R}^d$, We denote by $\Pi_x$ the law of $\xi$ starting from $x$. The semigroup of $\xi$ will be denoted by $\{T_t: t\geq 0\}$.
Denoted by $(T_t)_{t\geq 0}$ the transition semigroup of $\xi$.
%In this paper, we consider a branching mechanism of the form  
%\begin{equation}\label{mechanism}
%\psi(\lambda)=-\alpha \lambda + \lambda^{(1+\beta)}, \lambda \geq 0
%Where $\alpha = -\psi'(0+)>0$ and $\beta \in (0,1) $.
Let $\psi$ be a function on $\mathbb C_+:= \{x+iy: x\in [0,\infty), y\in \mathbb R\}$ with

@@

    \quad z \in \mathbb C_+,

@@

%Let $\mathcal{M}(\mathbb{R}^d)$ be the space of finite measures on $\mathbb{R}^d$. 

@@

%We say a $\mathcal{M}(\mathbb{R}^d)$-value branching Markov process $X=\{(X_t)_{t\geq 0},\mathbb{P}_{\mu}\}$ is a super Ornstein-Uhlenbeck process (super-OU process) with branching mechanism $\psi$, if for any $t \geq 0$, positive bounded measurable functions $f$ on $\mathbb{R}^d$ and any $\mu \in \mathcal{M}(\mathbb{R}^d)$, we have 
%\begin{equation} \label{super}
%    \mathbb{P}_{\mu}(e^{-\langle f,X_t \rangle})=e^{-\langle u_f(\cdot , t), \mu \rangle},
%where  $u_f(\cdot , t)$ is the unique locally bounded positive solution to the equation
%\begin{equation}\label{eq1}
%     u_f(x , t) + \Pi_x \left( \int_0^t\psi(u_f(\xi_s,t-s))~ds\right) =\Pi_x [f(\xi_t)],
%In this paper, we write $\int f(x)\mu(dx)$ as $\langle f,\mu\rangle$. Put $\|\mu\|=\langle 1,\mu\rangle$. We assume that the parameter $\alpha$ in branching mechanism $\psi$ is larger than zero, i.e. $X$ is  supercritical.

@@

We say a $\mathcal{M}(\mathbb{R}^d)$-value Markov process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a super Ornstein-Uhlenbeck process (super-OU process) with branching mechanism $\psi$, if for each non-negative bounded measurable function $f$ on $\mathbb{R}^d$, we have

@@

%According to \cite[section 2]{Li2011Measure}, is equivalent to
According to \cite[section 2]{Li2011Measure}, the above is equivalent to
\begin{equation}\label{eq2}
     u_f(x , t) + \int_0^t T_{t-s}\psi(u_f(\cdot,s))(x)~ds=T_tf(x),\quad x \in \mathbb{R}^d,~ t\geq 0.
\end{equation}

    The existence of such superprocesses is well known, see \cite{EB} for instance. 
    %Let $||X_t||=\langle 1, X_t \rangle$ be the total mass of the process $X$ at time $t$, then $\{\|X_t\|; t \geq 0\}$ is a continuous-state branching process with branching mechanism $\psi$.  
    Note that $(\|X_t\|)_{t\geq 0}$ is a continuous-state branching process with branching mechanism $\psi$. 
    %The fact $\psi(\infty)=\infty$ implies that the probability of extinction event $D:=\{\lim_{t \rightarrow \infty}||X_t||=0\}$ is contained in $(0,1)$, see, for example,  \cite[section 10.2.2]{Kyprianou2014Fluctuations}. 
    The fact $\psi(\infty)=\infty$ implies that the probability of extinguish event $D:=\{\lim_{t \rightarrow \infty}||X_t||=0\}$ is contained in $(0,1)$, see \cite[Theorem 12.7]{Kyprianou2014Fluctuations} for example. 
    %Let $\alpha^{\ast}$ be the larger root of $\psi=0$, we have $$\mathbb{P}_{\mu}\left(\lim_{t\rightarrow \infty}\|X_t\|=0\right)=e^{-\alpha^{\ast}\|\mu\|}.$$
    In fact, 
\begin{equation}
    \mathbb{P}_{\mu} (\lim_{t \to \infty}\|X_t\|=0 )
    = e^{-\alpha^* \|\mu\|},
\end{equation}
    where $\alpha^* := \sup\{\lambda \geq 0: \psi(\lambda) = 0\}$.

%For any $f \in \mathcal{P}$, define the {\em Feyman-Kac semigroup}
    Define the \emph{Fenyman-Kac semigroup} by  
\begin{equation}\label{meansemigroup}
    T^{\alpha}_t f(x) 
    := \Pi_x [e^{\alpha t}f(\xi_t)],
    %\quad x\in \mathbb{R}^d,t\geq 0, 
    \quad x\in \mathbb{R}^d,t\geq 0, f\in \mathscr B^+(\mathbb R^d).
\end{equation}
%which is konwn as the {\em mean semigroup} of the superprocess $X$, in the sense that
    It is konwn that, see \cite[Proposition 2.27]{Li2011Measure} for example, $(T^\alpha_t)_{t\geq 0}$ is the \emph{mean semigroup} of $X$, in the sense that
\begin{equation}\label{meanformula}
    \mathbb{P}_{\mu}[\langle f, X_t \rangle] 
    = \langle T_t^\alpha f, \mu \rangle,
%new
    \quad t\geq 0, f\in \mathscr B^+(\mathbb R^d).
%end new
\end{equation}
%see \cite[Proposition 2.27]{Li2011Measure}. 
%Notice that $T^{\alpha}_t f =e^{\alpha t}T_t f$.
Notice that $T^{\alpha}_t =e^{\alpha t}T_t$ for each $t \geq 0$.

%The purpose of this paper is to establish some spatial central limit theorems for the super OU-process with stable branching \eqref{mechanism}. More precisely, consider the limit of 
%$$\frac{\langle f,X_t\rangle-\|X_t\|\langle f, \varphi \rangle}{F_t},$$
%we want to find $(F_t)_{t\geq0}$, for suitable test functions $f$, such that the former formula convergence to some non-degenerate random variable as $t\rightarrow \infty$.

%\subsection{OU semigroup and Eigenfunctions}
\subsection{OU semigroup}
({\bf Do we have a good reference about those following result about the OU semigroup?})
Recall that $\xi$ is an OU process with generator $L$. It is known that $\xi$ has an invariant density
\begin{equation}\label{invariantdensity}
    \varphi (x) 
    =\Big (\frac{b}{\pi \sigma^2}\Big )^{\frac{d}{2}}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big),\quad x\in \mathbb{R}^d.
\end{equation}
Let $L^2(\varphi):= \left\{ h: \int_{\mathbb{R}^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$, then $L^2(\varphi)$ is an Hilbert space with inner product
\begin{equation}
\langle f_1, f_2 \rangle_{\varphi} 
%= 
:=
\int_{\mathbb{R}^d}f_1(x)f_2(x)\varphi(x) dx, \quad f_1,f_2 \in L^2(\varphi).
\end{equation}

    %For $p=(p_1,p_2,...,p_d) \in \mathbb{Z}_+^{d}$, let $|p|=p_1+...+p_d$, $p!=p_1 \cdot ... \cdot p_n$ and $\partial x^p =\partial x_1^{p_1} \cdot ... \cdot \partial x_d^{p_d}$. We recall the Hermite polynomials $H_p$ in $\mathbb{R}^d$
    For each $p = (p_k)_{k = 1\dots d} \in \mathbb{N}_0^{d}$, let $|p|=\sum_{k=1}^d p_k$, $p!= \prod_{k= 1}^d p_k !$ and $\partial x^p = \prod_{k = 1}^d\partial x_k^{p_k}$. 
    The Hermite polynomials are defined by
\begin{equation}
    H_p(x)
    %:=(-1)^{|p|}e^{|x|^2} \frac{\partial ^{|p|}}{\partial x^p} \left ( e^{-|x|^2} \right ).
    :=(-1)^{|p|}\exp(|x|^2) \frac{\partial ^{|p|}}{\partial x^p} \exp(-|x|^2) ,
    \quad x\in \mathbb R^d, p \in \mathbb{N}_0^{d}.
\end{equation}
%It is known that, see \cite{GD} as an example, the eigenvalues of $L$ are $\{-bk: k =0,1,2,...\}$ and the eigenspace $A_k$ corresponding to $-bk$ is
%$$A_k = {\rm Span} \{\phi_p : |p|=k\},$$
It is known that, see \cite{GD} for example, the generator $L$ of OU process $\xi$ can be viewed as an operator 
%on $L^2(\phi)$ 
on $L^2(\varphi)$ 
with eigenvalues $\sigma(L)= \{-bk: k \in \mathbb N_0\}$.
For each $k \in \mathbb N_0$, the eigenspace $A_k$ corresponding to eigenvalue $-bk$ of this operator is
\begin{equation}
    A_k 
    %= \operatorname{Span} \{\phi_p : |p|=k\},
    = \operatorname{Span} \{\phi_p : p\in \mathbb N_0^d, |p|=k\},
\end{equation}
where
\begin{equation}\label{eigenfunction}
	\phi_p(x) 
    := \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{\sigma}x \Big),
    %\quad x\in \mathbb{R}^d, p\in \mathbb{Z}_+^d.
    \quad x\in \mathbb{R}^d, p\in \mathbb N_0^d.
\end{equation}
 %The function $\phi_p$ is an eigenfunction of $L$ corresponding to the eigenvalue $-b|p|$, and satisfies 
 It is known that 
\begin{equation}\label{semigroupformula}
    T_t\phi_p(x)
    =e^{-b|p|t}\phi_p(x),
    \quad t\geq 0, x\in \mathbb{R}^d, p\in \mathbb N_0^d.
\end{equation}
%Moreover, The polynomials $\{\phi_p(x)\}_{p \in \mathbb{Z}_+^d}$ form a complete orthonormal basis of $L^2(\varphi)$. Thus, for any $f\in L^2(\varphi)$, we have
Moreover, it is known that $\{\phi_p: p \in \mathbb N_0^d\}$ forms a complete orthonormal basis of $L^2(\varphi)$. 
Therefore, for each $f\in L^2(\varphi)$, 
\begin{equation}\label{semicomp1}
    f
    =\sum_{k=0}^{\infty}\sum_{|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p, 
    \quad \text{in~} L^2(\varphi).
\end{equation}
%where $a_p=\langle f, \phi_p \rangle_{\varphi}$. 
Let
\begin{equation}\label{order}
    \kappa(f)
    %:=\inf \left \{k\geq 0: \exists ~ p\in \mathbb{Z}_+^d,{\rm ~s.t.~}|p|=k {\rm ~and~}  a_p \neq 0\right \}
    :=\inf \left \{k\geq 0: \exists ~ p\in \mathbb{Z}_+^d,{\rm ~s.t.~}|p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}
\end{equation}
denote the order of function $f$ in $L^2(\varphi)$. Then $ \kappa(f)\geq 0$, in particular, the order of constant functions is zero.

In this paper, we consider functions in the space of functions of ploynomial growth $\mathcal{P}$ defined as
\begin{equation}
     \mathcal{P}
     %:=\big \{f\in \mathcal{B}(\mathbb{R}^d):\exists~ C, n>0, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
     :=\big \{f\in \mathcal{B}(\mathbb{R}^d):\exists~ C>0, n \in \mathbb N_0, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
\end{equation}
%It is easy to see that $\mathcal{P} \subset L^2(\phi)$. 
It is easy to see that $\mathcal{P} \subset L^2(\varphi)$. 
%What's more, 
According to \cite[Fact 1.2]{MM},
for any $f \in \mathcal{P}$, there exists $R \in \mathcal{P}$ such that for any $t\geq 0$,
\begin{equation}\label{semigroupineq}
    |T_tf(x)| \leq e^{-\kappa(f)bt}R(x).
\end{equation}
%That is to say the rate of decay of the semigroup depending on $\kappa(f)$. 
%The readers can find the prove in \cite[Fact 1.2]{MM}.

\subsection{Characteristic functions}
 Let $X$ be a super OU-process with initial configuration $\mu$. For any $f \in \mathcal{P}$,
replace $f$ by $-i\theta f$ in equations of \eqref{super} and \eqref{eq2}, we obtain that
\begin{equation}\label{characteristic}
    \mathbb{P}_{\mu}\left[\exp(i\theta \langle  f,X_t\rangle)\right]=e^{\langle w_f(\cdot,t,\theta),\mu\rangle}
\end{equation}
where $w_f(x,t,\theta)=\log \mathbb{P}_{\delta_x}e^{i\theta\langle f,X_t\rangle}$ satisfying the equation that
\begin{equation}\label{charequation}
    w_f(x,t,\theta)-\int_0^t T_{t-s} \left(\psi (-w_f(\cdot,s,\theta))\right)(x)ds=i\theta T_tf(x)
\end{equation}

Recall the branching mechanism $\psi$ and Feynman-Kac semigroup $T^{\alpha}_t$, and apply \cite[Proposition 2.9]{Li2011Measure} to \eqref{charequation}, we have that
\begin{equation}\label{chareq2}
        w_f(x,t,\theta)-\int_0^t T^{\alpha}_{t-s} \left( (-w_f(\cdot,s,\theta))^{1+\beta}\right)(x)ds=i\theta T^{\alpha}_t f(x)
\end{equation}

@@

\section{Preliminaries}
In this section, we will estimate the characteristic function and the $(1+\gamma)$-th moments of super OU-process, where $\gamma \in [0,\beta)$. Fix $g\in \mathcal{P}$ and for notational convenience we omit it in formulations of most of lemmas below.

>>>>

% supCLT3.tex 2018/8/25 by Zhenyao
% supCLT2.tex 2018/8/13 by Jianjie
% supCLT1.tex 2018/7/24 by Zhenyao

@@

\usepackage{comment}

@@

\email{zhaojianjie@pku.edu.cn}

@@

@@

\label{eq: OU generator}

@@

@@

Denote by $(T_t)_{t\geq 0}$ the transition semigroup of $\xi$.
%Let $\psi$ be a function on $\mathbb C_+:= \{x+iy: x\in [0,\infty), y\in \mathbb R\}$ with
Let $\psi$ be a function on $\mathbb R_+:= [0,\infty)$ with

@@

    %\quad z \in \mathbb C_+,
    \quad z \in \mathbb R_+,

@@

@@

@@

We say a $\mathcal{M}(\mathbb{R}^d)$-valued Markov process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a super Ornstein-Uhlenbeck process (super-OU process) with branching mechanism $\psi$, if for each non-negative bounded measurable function $f$ on $\mathbb{R}^d$, we have

@@

%deleted
%According to \cite[section 2]{Li2011Measure-valued}, the above is equivalent to
%\begin{equation}\label{eq2}
     %u_f(x , t) + \int_0^t T_{t-s}\psi(u_f(\cdot,s))(x)~ds=T_tf(x),\quad x \in \mathbb{R}^d,~ t\geq 0.
%end deleted

    The existence of such superprocesses is well known, see \cite{EB} for instance.
    Note that $(\|X_t\|)_{t\geq 0}$ is a continuous-state branching process with branching mechanism $\psi$.
    The fact $\psi(\infty)=\infty$ implies that the probability of extinguish event $D:=\{\lim_{t \rightarrow \infty}||X_t||=0\}$ is contained in $(0,1)$, see \cite[Theorem 12.7]{Kyprianou2014Fluctuations} for example.
    In fact,
\begin{equation}
    \mathbb{P}_{\mu} (\lim_{t \to \infty}\|X_t\|=0 )
    = e^{-\alpha^* \|\mu\|},
\end{equation}
    where $\alpha^* := \sup\{\lambda \geq 0: \psi(\lambda) = 0\}$.
%comment
    {\bf (Zhenyao: We should use \cite[Theorem 12.5]{Kyprianou2014Fluctuations} and talk about the probability of $D:= \{\exists t\geq 0,~\text{s.t.}~\|X_t\|=0\}$. Because we want to emphsis that our superprocess is non-presistent.)}
%end comment

    Define the \emph{Fenyman-Kac semigroup} by
\begin{equation}\label{meansemigroup}
    T^{\alpha}_t f(x)
    := \Pi_x [e^{\alpha t}f(\xi_t)],
    \quad x\in \mathbb{R}^d,t\geq 0, f\in \mathscr B^+(\mathbb R^d).
\end{equation}
    It is konwn that, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(T^\alpha_t)_{t\geq 0}$ is the \emph{mean semigroup} of $X$, in the sense that
\begin{equation}\label{eq:meanformula}
    \mathbb{P}_{\mu}[\langle f, X_t \rangle]
    = \langle T_t^\alpha f, \mu \rangle,
    \quad t\geq 0, f\in \mathscr B^+(\mathbb R^d).
\end{equation}
Notice that $T^{\alpha}_t =e^{\alpha t}T_t$ for each $t \geq 0$.

\subsection{OU semigroup}
%moved and modified from below
    In tihs subsection, we recall some results on the spectrum property of the OU operator $L$ from \cite{GD}.
%end moved and modified from below
    %Recall that $\xi$ is an OU process with generator $L$. It is known that $\xi$ has an invariant density
    Let $\xi$ be an OU process with generator $L$ given by \eqref{eq: OU generator}. 
    %It is known that $\xi$ has an invariant density
    It is known that $\xi$ has an invariant measure
\begin{equation}
\label{invariantdensity}
    %\varphi (x)
    \varphi(x)dx
    %=\Big (\frac{b}{\pi \sigma^2}\Big )^{\frac{d}{2}}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big),\quad x\in \mathbb{R}^d.
    =\Big (\frac{b}{\pi \sigma^2}\Big )^{d/2}\exp \Big(-\frac{b}{\sigma^2}|x|^2 \Big)dx,
    \quad x\in \mathbb{R}^d.
\end{equation}
    Let $L^2(\varphi):= \left\{ h: \int_{\mathbb{R}^d} |h(x)|^2 \varphi(x) dx < \infty \right\}$, then $L^2(\varphi)$ is an Hilbert space with inner product
\begin{equation}
    \langle f_1, f_2 \rangle_{\varphi}
    := \int_{\mathbb{R}^d}f_1(x)f_2(x)\varphi(x) dx, \quad f_1,f_2 \in L^2(\varphi).
\end{equation}
%moved to above
    %In tihs subsection, we recall some results on the spectrum in $L^2(\varphi)$ of the operator $L$, more details can be found in \cite{GD}.
%end moved to above
    %For each $p = (p_k)_{k = 1\dots d} \in \mathbb{N}_0^{d}$, let $|p|=\sum_{k=1}^d p_k$, $p!= \prod_{k= 1}^d p_k !$ and $\partial x^p = \prod_{k = 1}^d\partial x_k^{p_k}$.
    For each $p = (p_k)_{k = 1}^d \in \mathbb{N}_0^{d}$, let $|p|=\sum_{k=1}^d p_k$, $p!= \prod_{k= 1}^d p_k !$ and $\partial x^p = \prod_{k = 1}^d\partial x_k^{p_k}$.
    The Hermite polynomials are defined by
\begin{equation}
    H_p(x)
    :=(-1)^{|p|}\exp(|x|^2) \frac{\partial ^{|p|}}{\partial x^p} \exp(-|x|^2) ,
    \quad x\in \mathbb R^d, p \in \mathbb{N}_0^{d}.
\end{equation}
    It is known that the generator $L$ of OU process $\xi$ can be viewed as an operator on $L^2(\varphi)$ with eigenvalues $\sigma(L)= \{-bk: k \in \mathbb N_0\}$.
    %For each $k \in \mathbb N_0$, the eigenspace $A_k$ corresponding to eigenvalue $-bk$ of this operator is
    For each $k \in \mathbb N_0$, the eigenspace $A_k$ corresponding to eigenvalue $-bk$ is
\begin{equation}
    A_k
    %= \operatorname{Span} \{\phi_p : |p|=k\},
    = \operatorname{Span} \{\phi_p : p\in \mathbb N_0^d, |p|=k\},
\end{equation}
where
\begin{equation}\label{eigenfunction}
	\phi_p(x)
    := \frac{1}{\sqrt{ p! 2^{|p|} }} H_p \Big(\frac{ \sqrt{b} }{\sigma}x \Big),
    %\quad x\in \mathbb{R}^d, p\in \mathbb{Z}_+^d.
    \quad x\in \mathbb{R}^d, p\in \mathbb N_0^d.
\end{equation}
 %The function $\phi_p$ is an eigenfunction of $L$ corresponding to the eigenvalue $-b|p|$, and satisfies
 It is known that
\begin{equation}\label{semigroupformula}
    T_t\phi_p(x)
    =e^{-b|p|t}\phi_p(x),
    \quad t\geq 0, x\in \mathbb{R}^d, p\in \mathbb N_0^d.
\end{equation}
    %Moreover, it is known that $\{\phi_p: p \in \mathbb N_0^d\}$ forms a complete orthonormal basis of $L^2(\varphi)$.
    Moreover, it is known that $\{\phi_p: p \in \mathbb N_0^d\}$ forms a complete orthogonal basis for $L^2(\varphi)$.
    %Therefore, for each $f\in L^2(\varphi)$,
    That is, for each $f\in L^2(\varphi)$,
\begin{equation}\label{semicomp1}
    f
    =\sum_{k=0}^{\infty}\sum_{|p|=k}\langle f, \phi_p \rangle_{\varphi} \phi_p,
    \quad \text{in~} L^2(\varphi).
\end{equation}
%Let
    Denote
\begin{equation}\label{order}
    \kappa(f)
    :=\inf \left \{k\geq 0: \exists ~ p\in \mathbb{Z}_+^d,{\rm ~s.t.~}|p|=k {\rm ~and~}  \langle f, \phi_p \rangle_{\varphi}\neq 0\right \}
\end{equation}
    %denote the order of function $f$ in $L^2(\varphi)$. Then $ \kappa(f)\geq 0$, in particular, the order of constant functions is zero.
    the order of function $f$ in $L^2(\varphi)$. 
    Then $ \kappa(f)\geq 0$. 
    In particular, the order of any constant function is zero.

    %In this paper, we consider functions in the space of functions of ploynomial growth $\mathcal{P}$ defined as
    In this paper, we consider the class of functions of ploynomial growth $\mathcal{P}$ defined by
\begin{equation}
    \mathcal{P}
    :=\big \{f\in \mathcal{B}(\mathbb{R}^d):\exists~ C>0, n \in \mathbb N_0, {\rm ~s.t.~} \forall x\in \mathbb{R}^d,~ |f(x)|\leq C(1+|x|)^n\big\}.
\end{equation}
    It is easy to see that $\mathcal{P} \subset L^2(\varphi)$.
    %According to \cite[Fact 1.2]{MM}, for any $f \in \mathcal{P}$, there exists $R \in \mathcal{P}$ such that for any $t\geq 0$,
    According to \cite[Fact 1.2]{MM}, for any $f \in \mathcal{P}$, there exists $R \in \mathcal{P}$ such that,
\begin{equation}
\label{eq:semigroupineq}
    |T_tf(x)| 
    \leq e^{-\kappa(f)bt} R(x),
    \quad t\geq 0, x\in \mathbb R^d.
\end{equation}

\subsection{Characteristic functions}
    %Let $X$ be a super OU-process with initial configuration $\mu$. 
%new added
    Let the Gamma function $\Gamma$ be defined by
\begin{equation}
    \Gamma (x) := \int_0^\infty t^{x-1} e^{-t}dt, 
    \quad x>0,
\end{equation}
and
\begin{align}
\label{eq: definition of Gamma function}
    \Gamma(x)
    := \int_0^\infty t^{x-1} \Big(e^{-t} - \sum_{k=0}^{n-1} \frac{(-t)^k}{k!}\Big) dt,
    \quad -n< x< -n+1, n\in \mathbb N.
\end{align}
    Then it is elementary to verify that
\begin{equation}
    \Gamma(x+1) = x\Gamma(x),
    \quad x>0~\text{or}~-n< x< -n+1, n\in \mathbb N.
\end{equation}

    Fix a $\beta \in (0,1)$.
    According to \cite[Theorem 3.2. \& Theorem 3.5.]{SchillingSongVondracek2010Bernstein}, we can verify that the following function:
\begin{equation}
    z
    \mapsto z^{\beta}
    := \int_0^\infty (e^{-zy}-1) \frac{dy}{\Gamma(-\beta)y^{1+\beta}}, 
    \quad z\in \mathbb C_+,
\end{equation}
\begin{itemize}
\item
    is an extension of the real function $x\mapsto x^{\beta}$ on $[0,\infty)$;
\item
    is continuous in $\mathbb C_+$;
\item 
    is holomorphic in $\mathbb C_+^0$.
\end{itemize}
    According to Lemma \ref{lem: extension lemma for branching mechanism} in the Appendix, we can verify that the following function:
\begin{equation}
\label{eq: stable branching on C+}
    z\mapsto 
    z^{1+\beta} 
    := \int_0^\infty (e^{-zy}-1+zy)\frac{dy}{\Gamma(-1-\beta)y^{2+\beta}},
    \quad z\in \mathbb C_+,
\end{equation}
\begin{itemize}
\item
    is an extension of the real function $x\mapsto x^{1+\beta}$ on $[0,\infty)$;
\item
    is continuous in $\mathbb C_+$;
\item 
    is holomorphic in $\mathbb C_+^0$.
\end{itemize}
    Moreover, according to \eqref{eq: path integration representation of h}, for any $C^1$ path $\gamma:[0,1]\mapsto \mathbb C_+$,
\begin{align}
\label{eq: integration formula for 1+beta-th power of z}
    &\gamma(1)^{1+\beta} - \gamma(0)^{1+\beta} 
    = \int_0^1 \gamma'(\theta)d\theta \int_{(0,\infty)}(1-e^{-\gamma(\theta)y})\frac{ydy}{\Gamma(-1-\beta)y^{2+\beta}}
    \\&=\int_0^1 \gamma'(\theta)d\theta \int_{(0,\infty)}(1-e^{-\gamma(\theta)y})\frac{(-1-\beta)dy}{\Gamma(-\beta)y^{1+\beta}} 
    = \int_0^1 (1+\beta) \gamma(\theta)^{\beta} \gamma'(\theta)d\theta.
\end{align}
    This indicates that the derivative of $z\mapsto z^{1+\beta}$ is $z\mapsto (1+\beta)z^{\beta}$ on $\mathbb C^0_+$.
\begin{lem}
\label{lem: Lip of power function}
    There is a constant $C_0 > 0$ such that for any $z_0,z_1 \in \mathbb C_+$,
\[
    |z_0^{1+\beta} - z_1^{1+\beta}| 
    \leq C_0(|z_0|^{\beta}+|z_1|^{\beta})|z_0 - z_1|.
\]
\end{lem}
\begin{proof}
    Notice that
\begin{align}
\label{eq: upper bound for beta power of z}
    &|z^{\beta}|
    = \Big|\int_0^\infty (e^{-zy}-1) \frac{dy}{\Gamma(-\beta)y^{1+\beta}}\Big| 
    \\&\leq \frac{1}{|\Gamma(-\beta)|}\int_0^\infty \frac{2\wedge (|z|y)}{y^{1+\beta}}dy
    \\&= \frac{|z|^{\beta}}{|\Gamma(-\beta)|}\int_0^\infty \frac{2\wedge t}{t^{1+\beta}}dt =: c_0 |z|^{\beta},
    \quad z\in \mathbb C_+.
\end{align}
    Define a path $\gamma: [0,1] \to \mathbb C_+$ such that
\[
    \gamma(\theta) 
    = z_0 (1-\theta) + \theta z_1,
    \quad \theta \in [0,1].
\]
    Then, according to \eqref{eq: integration formula for 1+beta-th power of z}, we have
\begin{align}
    |z_0^{1+\beta} - z_1^{1+\beta}| 
    &\leq (1+\beta) \int_0^1 |\gamma(\theta)^{\beta}|\cdot |\gamma'(\theta)|d\theta
    \leq (1+\beta) c_0 \sup_{\theta \in [0,1]} |\gamma(\theta)|^{\beta} \cdot |z_1-z_0|
    \\&\leq (1+\beta) c_0 ( |z_1|^{\beta}+|z_0|^{\beta} ) |z_1-z_0|.
    \qedhere
\end{align}
\end{proof}

    Let $X$ be the super OU-process discussed in the previous subsections.
    Its branching mechanism $\psi$ can be extended in the following way: $\psi(z) := -\alpha z + z^{1+\beta}$ for $z\in \mathbb C_+$. 
    Then according to the above analysis, $\psi$ is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0:=\{x+iy:x \in (0,\infty), y\in \mathbb R\}$ with derivative
\begin{equation}
\label{eq: deriavetive of the Poission part}
    \psi'(z) := -\alpha + (1+\beta)z^{\beta},
    \quad z\in \mathbb C_+.
\end{equation}
Write $\psi_0(z) = \psi(z) + \alpha z$ and $\psi'_0(z) = \psi'(z) + \alpha$.
%end new added
    %For any $f \in \mathcal{P}$, replace $f$ by $-i\theta f$ in equations of \eqref{super} and \eqref{eq2}, we obtain that
%\begin{equation}\label{characteristic}
    %\mathbb{P}_{\mu}\left[\exp(i\theta \langle  f,X_t\rangle)\right]=e^{\langle w_f(\cdot,t,\theta),\mu\rangle}
%\end{equation}
%where $w_f(x,t,\theta)=\log \mathbb{P}_{\delta_x}e^{i\theta\langle f,X_t\rangle}$ satisfying the equation that
%\begin{equation}\label{charequation}
    %w_f(x,t,\theta)-\int_0^t T_{t-s} \left(\psi (-w_f(\cdot,s,\theta))\right)(x)ds=i\theta T_tf(x)
%\end{equation}
    For each $t\in [0,\infty), x\in \mathbb E$ and $f \in \mathcal{P}$, denote by $w_f(x,t,\theta):= \operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta X_t(f)}]$ the characteristic exponent of $\{X_t(f); \mathbb P_{\delta_x}\}$
    (For percise definition, see the argument in Subsection \ref{sec: definition of characteristic exponent} of Appendix).
    From \eqref{eq: -v has positive real part}, we know that $- w_f(x,t,\theta)$ taks values in $\mathbb C_+$.
    Furthermore, we know from Proposition \ref{sec: definition of characteristic exponent} that
%delete
%\begin{equation}\label{characteristic}
    %\mathbb{P}_{\mu}[e^{i\theta X_t(f)}]
    %=e^{\langle w_f(\cdot,t,\theta),\mu\rangle},
    %\quad t\in [0,\infty), \mu\in \mathcal M(\mathbb R^d), f\in \mathcal P, \theta \in \mathbb R.
%\end{equation}
    %where $w_f(x,t,\theta)$ satisfies the equation
\begin{align}\label{charequation}
    w_f(x,t,\theta)-\int_0^t T_{t-s} \psi \big(-w_f(\cdot,s,\theta)\big)(x)ds
    =i\theta T_tf(x),
    \\ \quad t\in [0,\infty), \mu\in \mathcal M(\mathbb R^d), f\in \mathcal P, \theta \in \mathbb R.
\end{align}
and
\begin{align}
\label{eq:chareq2}
    %w_f(x,t,\theta)-\int_0^t T^{\alpha}_{t-s} \left( (-w_f(\cdot,s,\theta))^{1+\beta}\right)(x)ds=i\theta T^{\alpha}_t f(x),
    w_f(x,t,\theta)-\int_0^t T^{\alpha}_{t-s} \psi_0(-w_f(\cdot,s,\theta))(x)ds=i\theta T^{\alpha}_t f(x),
    \\ \quad t\in [0,\infty), \mu\in \mathcal M(\mathbb R^d), f\in \mathcal P, \theta \in \mathbb R.
\end{align}
%new added
%end new added
%begin comments
    {\bf Zhenyao: There are notation inconsistency in the Appendix and other suctions. Mainly on the branching mechanism: In the appendix, we use
\[
    \psi(x,z)= -\beta(x)z+\alpha(x)z^2 + \int_0^t \dots;
\]
    But in other subsections we use
\[
    \psi(z) = - \alpha z + z^{1+\beta}.
\]
    Readers can easily be confused by which $\alpha$ and $\beta$ we mean in the context.

    Another inconsistency is the notation for the characteristic exponent $\operatorname{Log} \mathbb P_{\delta_x}[e^{i\theta X_t(f)}]$. In the appendix we use $v_f(t,x,\theta)$, but in other subsection we use $w_f(x,t,\theta)$. I recommended to use $v_f$ because I would like that $w$ be reserved for representing canonical element in some measurable spaces. Also, I would like to use $(t,x)$ instead of $(x,t)$ because it make more sense to put the ``time parameter t" first. ($(t,x)$ and $(x,t)$ are both used by different authors.)

    Though I recommended all those changes, I did not try to make them in this version (in order to not mess things up). I would like Jianjie to decide which set of notations is better. Overall, I am fine with any set of notations as long as they are consistent with each other and don't raise any confusions.}
%end comments

@@

\section{Preliminaries}
In this section, we will estimate the characteristic function and the $(1+\gamma)$-th moments of super OU-process, where $\gamma \in [0,\beta)$. 
%For notational convenience, we always fix $g\in \mathcal{P}$ in the following sections, correspondingly, there exists $R\in\mathcal{P}$ such that 
    In this section, we fix a $g\in \mathcal{P}$. 
    According to \eqref{eq:semigroupineq}, there exists an $R_0\in\mathcal{P}$ such that 
\begin{align}
     %|T_tg|\leq T_t|g|\leq e^{-\kappa(g)bt}R.
     |T_tg|(x)
     \leq e^{-\kappa(g)bt}R_0(x),
     \quad t\geq 0,x\in E.
\end{align}
%new added
Taking $T_s$ on the both side of the above inequality (since it is a positive operator), we have that there exists $R \in \mathcal P$ such that
\begin{align}
\label{eq:gcontrol}
    T_s|T_t g|(x) 
    \leq e^{-\kappa(g)bt} R(x), 
    \quad t\geq 0,s\geq 0,x\in E.
\end{align}
%end new added
